Supplementary Material \--- Laves polyhedrons in synthetic tennantite, Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}, and the lattice dynamics

### 2021-01-16 SM/paper_tennantite.tex
Refined atomic parameters and refined anisotropic ADP added

A~spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study.
Table~\ref{tab:inter_dist} and in~Table~\ref{tab:crystallographic_information} show the~comparison of previous results\cite{yaroslavzev2019} and the spherical shape single-crystal structural data.

@@

>>>>

A~spherical shape single-crystal sample of Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}  was prepared for the anisotropic extinction study.
Table~\ref{tab:inter_dist} and in~Table~\ref{tab:crystallographic_information} show the~comparison of previous results\cite{yaroslavzev2019} and the spherical shape single-crystal structural data. Refined atomic parameters and refined anisotropic ADP are presented in~Table~\ref{tab:atom_param} and in~Table~\ref{tab:ref_adp}.

@@

\begin{table}
\caption{\label{tab:atom_param}
Refined atomic parameters in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}. 
Cu(1): $\frac{1}{2}$,$\frac{1}{4}$,0; Cu(2): x,0,0; Cu(21): x,y,y; As(1): x,x,x;  S(1): x,y,–y; S(2): 0,0,0.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
&
Averaged, \AA  &
Extinct, \AA  &
Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
Occupancy, Cu(2)                          & 0.660(8)    & 0.670(5)     & 0.679(11)  \\
x, Cu(2)                                  & 0.2181(6)   & 0.2185(4)    & 0.2172(5)  \\
x, Cu(21)                                 & 0.2113(15)  & 0.2111(10)   & 0.2149(12) \\
y, Cu(21)                                 & 0.0617(17)  & 0.0601(9)    & 0.0662(19) \\
x, As(1)                                  & 0.24141(10) & 0.24141(6)   & 0.24162(4) \\
x, S(1)                                   & 0.3566(2)   & 0.35709(12)  & 0.35722(7) \\
–y, S(1)                                  & 0.11809(14) & 0.11835(8)   & 0.11854(6) \\
Ueq$\times$10\textsuperscript{4}, Cu(1)   & 212(3)      & 214(2)       & 184(3)     \\
Ueq$\times$10\textsuperscript{4}, Cu(2)   & 399(8)      & 415(5)       & 339(5)     \\
Ueq$\times$10\textsuperscript{4}, Cu(21)  & 543(22)     & 573(13)      & 420(3)     \\
Ueq$\times$10\textsuperscript{4}, As(1)   & 146.8(5)    & 147.1(3)     & 114.0(7)   \\
Ueq$\times$10\textsuperscript{4}, S(1)    & 151.6(15)   & 152.5(10)    & 111.0(13)  \\
Ueq$\times$10\textsuperscript{4}, S(2)    & 164.6(14)   & 167.5(9)     & 160(7)     \\

\begin{table}
\caption{\label{tab:ref_adp}
Refined anisotropic ADP in Cu\textsubscript{12}As\textsubscript{4}S\textsubscript{13}.}
\centering
\resizebox{\columnwidth}{!}{
\begin{tabular}{lccc}
&
Averaged, \AA  &
Extinct, \AA  &
Ref.~\cite{yaroslavzev2019} at 293~K, \AA  \\
$U_{11}$, $U_{33}\times$10\textsuperscript{4}, Cu(1)             & 176(4)      & 179(3)     & 146(3)  \\
$U_{22}\times$10\textsuperscript{4}, Cu(1)                       & 284(9)      & 284(6)     & 248(7)  \\
$U_{11}\times$10\textsuperscript{4}, Cu(2)                       & 158(7)      & 148(9)     & 117(6)  \\
$U_{22}$, $U_{33}\times$10\textsuperscript{4}, Cu(2)             & 493(14)     & 537(14)    & 451(9)  \\
$U_{11}\times$10\textsuperscript{4}, Cu(21)                      & 210(20)     & 193(20)    & 205(18)  \\
$U_{22}$, $U_{33}\times$10\textsuperscript{4}, Cu(21)            & 660(70)     & 710(40)    & 490(60)  \\
$U_{12}$, $U_{13}\times$10\textsuperscript{4}, Cu(21)            & –140(40)    & –70(30)    & –170(30)  \\
$U_{23}\times$10\textsuperscript{4}, Cu(21)                      & 470(80)     & 530(50)    & 290(60)  \\
$U_{11}\times$10\textsuperscript{4}, S(1)                        & 134(4)      & 133(3)     & 90(3)  \\
$U_{22}$, $U_{33}\times$10\textsuperscript{4}, S(1)              & 163(2)      & 163.2(16)  & 119.9(18)  \\
$U_{12}$, $-U_{13}\times$10\textsuperscript{4}, S(1)             & –19.7(18)   & –22.0(14)  & –23.6(14)  \\
$U_{23}\times$10\textsuperscript{4}, S(1)                        & 2(3)        & 3(2)       & –8(2)  \\
$U_{11}$, $U_{22}$, $U_{33}\times$10\textsuperscript{4}, S(2)    & 166(4)      & 169(3)     & 128(3)  \\
$U_{11}$, $U_{22}$, $U_{33}\times$10\textsuperscript{4}, As(1)   & 151.9(15)   & 149.0(11)  & 112.8(13)  \\
$U_{12}$, $U_{13}$, $U_{23}\times$10\textsuperscript{4}, As(1)   & 1.4(12)     & 0.1(9)     & –1.6(10)  \\
